The demographic costs of sexually antagonistic selection in partially selfing populations

### 2021-12-17 doc/SA-Hermaphrodites-wDemography-R1.tex
Minor additional edits

\textcolor{blue}{While significant efforts have been made to predict when SA polymophisms can be maintained and to detect SA genetic variation from empirical data, much less consideration has been given to the demographic consequences of the maladaptation caused by SA selection}. Most population genetic models, including models of the maintenance of SA polymorphisms, keep track of the relative fitnesses of genotypes in populations of constant (and often infinite) size, and do not consider the population dynamical consequences of evolutionary change. In reality, these genotypic fitnesses emerge from myriad processes acting throughout the life-history of individuals \textcolor{blue}{which link genotype distributions to population dynamics (e.g., \citealt {johnston2013life, merot2020balancing}). Over the past 50 years, a rich field of eco-evolutionary dynamics has developed which seeks to jointly model the genetic and demographic processes involved in evolutionary change. In particular, theoretical models combining population genetics with density-dependent population growth \citep{roughgarden1971density} and stage-structured populations (consolidated in \citealt{Charlesworth_1994}) paved the way toward understanding the demographic changes accompanying allele frequency changes due to selection. Extensions of these theories to study life-history evolution \citep{orive1995senescence, orive2001somatic}, spatial structure \citep{ronce2000kin}, kin selection \citep{rousset2004genetic}, and quantitative traits \citep[e.g.,][]{coulson2006putting, barfield2011evolution, childs2016evolution, orive2017effects} all highlight the often counterintuitive demographic consequences of adaptive evolution that are orten missed by classical population genetics models (comprehensively reviewed by \citealt{fussmann2007eco} and \citealt{govaert2019eco}).}

>>>>

\textcolor{blue}{While significant efforts have been made to predict when SA polymophisms can be maintained and to detect SA genetic variation from empirical data, much less consideration has been given to the demographic consequences of the maladaptation caused by SA selection}. Most population genetic models, including models of the maintenance of SA polymorphisms, keep track of the relative fitnesses of genotypes in populations of constant (and often infinite) size, and do not consider the population dynamical consequences of evolutionary change. In reality, these genotypic fitnesses emerge from myriad processes acting throughout the life-history of individuals \textcolor{blue}{which link genotype distributions to population dynamics (e.g., \citealt {johnston2013life, merot2020balancing}). Over the past 50 years, a rich field of eco-evolutionary dynamics has developed which seeks to jointly model the genetic and demographic processes involved in evolutionary change. In particular, theoretical models combining population genetics with density-dependent population growth \citep{roughgarden1971density} and stage-structured populations (consolidated in \citealt{Charlesworth_1994}) paved the way toward understanding the demographic changes accompanying allele frequency changes due to selection. Extensions of these theories to study life-history evolution \citep{orive1995senescence, orive2001somatic}, spatial structure \citep{ronce2000kin}, kin selection \citep{rousset2004genetic}, and quantitative traits \citep[e.g.,][]{coulson2006putting, barfield2011evolution, childs2016evolution, orive2017effects} all highlight the often counterintuitive demographic consequences of adaptive evolution that are often missed by classical population genetics models (comprehensively reviewed by \citealt{fussmann2007eco} and \citealt{govaert2019eco}).}
